### 2022-08-29 manuscript/manuscript.tex
new method eval

>>>>

BGS as evolution around the static features of the genome. Due to the slow rate
of genomic structural evolution, much of the genome can be treated as static
throughout the genome. These regions are under differing levels of selective
constraint, which induces background selection at neighboring regions.
